---
title: "Cabbages"
author: "Daniel A Soria Zuniga"
date: "6-12-2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))

basicCN + geom_boxplot()
```

The Vitc differnce between the cult c39 and cult c52 is that on avarage cultc53 posseses more VitC as we can tell from the box plots, this helps us fairly evaluate the median difference between the both cultivations.

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

From this we are able to keep the same analisis that the c52 cultivation does have or carry more VitC compared to the toher cultivation of c39.
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
favstats(Cult~VitC,data=veggy)
```
This allows us to explore the mean of of the number of vitamin that each one would carry.
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion
My conclusion would be that the cultivation of c52 did in fact have more VitC that that cultivated of c39 , this is seen throughout the box plots and as we are able to differentate the mean throughout the different number of graphs, so yes as far as we are able to tell c52 did have more VitC.
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
